\documentclass[a4paper,11pt]{article}
\RequirePackage[T1]{fontenc}

\usepackage{times}
\usepackage{calc}
\usepackage[shortcuts]{extdash}

\usepackage{graphicx}

\reversemarginpar

\usepackage[paper=letterpaper,
            marginparwidth=1.1in,     % Length of section titles
            marginparsep=.075in,       % Space between titles and text
            margin=0.5in,               % 1 inch margins
            tmargin=0.65in,
            bmargin=0.8in,
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}

\usepackage{xcolor}
\definecolor{lafayette}{RGB}{102,0,0}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{0em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin=\bibhang,%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=[\arabic*],resume,leftmargin={\bibhang+\widthof{[999]}},%
        itemindent=-\bibhang,
        itemsep=0.05in,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother
\usepackage[english]{babel}

\usepackage{fancyhdr,lastpage}

\pagestyle{fancy}
\fancyhf{}                                    % clear all header/footer fields
\fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}            % no header rule
\renewcommand{\footrulewidth}{0pt}            % no footer rule
  % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\renewcommand{\section}[1]{\pagebreak[3]%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\hyphenpenalty=10000\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

\newcommand*\fixendlist[1]{%
    \expandafter\let\csname preFixEndListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixEndListend#1\endcsname\vspace{-0.6\baselineskip}}}

\let\originalItem\item
\newcommand*\fixouterlist[1]{%
    \expandafter\let\csname preFixOuterList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\def\item{\pagebreak[2]\oldItem}\csname preFixOuterList#1\endcsname}
    \expandafter\let\csname preFixOuterListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\let\item\oldItem\csname preFixOuterListend#1\endcsname}}
\newcommand*\fixinnerlist[1]{%
    \expandafter\let\csname preFixInnerList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\let\item\originalItem\csname preFixInnerList#1\endcsname}
    \expandafter\let\csname preFixInnerListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixInnerListend#1\endcsname\let\item\oldItem}}

\newlist{outerlist}{itemize}{3}
    \setlist[outerlist]{label=\enskip\textbullet,leftmargin=*}
    \fixendlist{outerlist}
    \fixouterlist{outerlist}

\newlist{lonelist}{itemize}{3}
    \setlist[lonelist]{label=\enskip\textbullet,leftmargin=*,partopsep=0pt,topsep=0pt}
    \fixendlist{lonelist}
    \fixouterlist{lonelist}

\newlist{innerlist}{itemize}{3}
    \setlist[innerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixinnerlist{innerlist}

\newlist{loneinnerlist}{itemize}{3}
    \setlist[loneinnerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixendlist{loneinnerlist}
    \fixinnerlist{loneinnerlist}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\usepackage{doi}
\usepackage{url}

\usepackage[useregional]{datetime2}

\urlstyle{same}
\providecommand*\emaillink[1]{\nolinkurl{#1}}
\providecommand*\email[1]{\href{mailto:#1}{\emaillink{#1}}}


% Icons for contact info
\usepackage{fontawesome5}    % email, github, link, etc.
\usepackage{academicons}     % ORCID, Google Scholar, ResearchGate, etc.

\begin{document}

 {\hspace*{-\marginparsep minus \marginparwidth}%
\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
\centering
{\LARGE \bfseries {Sayorn Chin}}\\
\vspace{0.2cm}
%Department of Economics, Lafayette College\\
%305 Simon Center for Economics and Business\\
\textcolor{lafayette}{\faIcon{envelope}~\href{mailto:chins@lafayette.edu}{chins@lafayette.edu}} |
\textcolor{lafayette}{\faLink~\href{https://schinlfc.github.io}{schinlfc.github.io}} |
\textcolor{lafayette}{\faGithub~\href{https://github.com/schinlfc}{schinlfc}} |
\textcolor{lafayette}{\faOrcid~\href{https://orcid.org/0000-0002-5745-8595}{0000-0002-5745-8595}} |
\textcolor{lafayette}{\faGraduationCap~\href{https://scholar.google.com/citations?user=Yx02X_IAAAAJ&hl=en}{Google Scholar}} \\
Department of Economics, Lafayette College\\
Simon Center for Economics and Business\\
730 High Street, Easton, PA 18042 USA

\vspace{0.2cm}
Last Update: \DTMdisplaydate{\year}{\month}{\day}{-1}
\rule{\columnwidth}{1.2pt}
\end{minipage}}

 \vspace{0.2cm}


\section{Visa Status}

\textbf{Cambodia:} Citizenship, \textbf{United States:} Permanent Resident

\section{Current Positions}

\textbf{Assistant Professor},
\href{https://economics.lafayette.edu/faculty-and-staff/}{Department of Economics, Lafayette College}
\hfill {Jul. 2023 -- Present}

\vspace{0.1cm}

\textbf{Data Science Fellow Affiliate},
\href{https://www.mountaindatagroup.com/}{Mountain Data Group}
\hfill {Jun. 2023 -- Present}


\section{Previous Positions}
\textbf{Data Scientist},
\href{https://www.mountaindatagroup.com/}{Mountain Data Group}
\hfill {May 2021 -- May 2023}

\vspace{0.1cm}

\textbf{Graduate Teaching Instructor},
\href{https://economics.colostate.edu/}{Colorado State University}
\hfill {Jul. 2020 -- May 2023}

\vspace{0.1cm}

\textbf{Graduate Teaching Assistant},
\href{https://economics.colostate.edu/}{Colorado State University}
\hfill {Aug. 2017 -- May 2020}

\vspace{0.1cm}

\textbf{Finance Assistant},
\href{https://www.coloradocollege.edu/offices/finance/}{Colorado College}
\hfill {Feb. 2016 -- Jan. 2017}

\vspace{0.1cm}

\textbf{Data Research Analyst},
\href{https://www.coloradocollege.edu/offices/qrc/}{Colorado College}
\hfill {Jan. 2016 -- May 2016}


\section{Education}

\textbf{Ph.D., Economics},
\href{https://economics.colostate.edu/}{Colorado State University}
\hfill {2023}

\vspace{0.1cm}

\textbf{M.A., Economics},
\href{https://economics.colostate.edu/}{Colorado State University}
\hfill {2019}

\vspace{0.1cm}

\textbf{B.A., Mathematical Economics},
\href{https://www.coloradocollege.edu/academics/dept/economics/}{Colorado College}
\hfill {2017}

\section{Research Output}

\textbf{Peer-Reviewed Publications: Economics}
\begin{enumerate}[leftmargin=*, label={[\arabic*]}]
\item Chin, S., \& Miller, R. (2026). Beyond income: Health, wealth, and racial welfare gaps among older Americans. \href{https://doi.org/10.1215/00703370-12460649}{\emph{Demography}}, \emph{63}(1), 187–211.
\item An, Y., Chin, S., \& Miller, R. (2025). Growing old in rural America: Measuring late-life health and economic well-being. \href{https://doi.org/10.1016/j.jeoa.2025.100565}{\emph{The Journal of the Economics of Ageing}}, \emph{31}, 100565.
\item Miller, R., Chin, S., \& Sedai, A. K. (2022). The welfare cost of late-life depression. \href{https://doi.org/10.1016/j.jebo.2022.10.001}{\emph{Journal of Economic Behavior \& Organization}}, \emph{204}, 15–36.
\end{enumerate}

\textbf{Peer-Reviewed Publications: Public Health}
\begin{enumerate}[leftmargin=*, label={[\arabic*]}]
\item Perry, T., \& Chin, S. (2026). The unregulated rise of kratom drinks: Emerging challenges and policy recommendations. \href{https://doi.org/10.1177/00333549251403378}{\emph{Public Health Reports}}, 1–6.
\item Perry, T., \& Chin, S. (2026). Kratom drinks and consumption trends: Insights from Reddit. \href{https://doi.org/10.1080/14659891.2025.2481069}{\emph{Journal of Substance Use}}, \emph{31}(1), 124–132.
\item Perry, T., \& Chin, S. (2025). Kratom beverages online: Marketing narratives, content, dosing, and potential risks. \href{https://doi.org/10.1080/10826084.2025.2592879}{\emph{Substance Use \& Misuse}}, 1–4.
\end{enumerate}

\textbf{Peer-Reviewed Publications: Economics Pedagogy}
\begin{enumerate}[leftmargin=*, label={[\arabic*]}]
    \item Chin, S., Io, K., K\i r\c{s}anl\i, F., \& Perry, T. (2026). From cheating to learning: AI integration in introductory economics. \href{https://doi.org/10.58311/jeconteach/9e4dd0ab8f5c89e19fdf8ca2e1a96d370b31a0fe}{\emph{Journal of Economics Teaching}}, \emph{11}(2), 208–228.
\end{enumerate}

\clearpage

\textbf{Working Papers}
\begin{enumerate}[leftmargin=*, label={[\arabic*]}]
\item Loss or Gain from Separation? Wealth and Child Mental Health in Divorce Dynamics, with Solano Caffarena, Swarup Joshi, and Ashish Sedai. \textit{Under Review}.
\item The Compensation of Conscience, with Sammy Zahran and Anders Fremstad. \textit{Under Review}.
\item The Longer Reach of Lead: Early Childhood Lead Exposure and Cognitive Ability Later-in-Life, with Christopher Keyes, Sammy Zahran, and David Mushinski. \textit{Under Review}.
\item Further Evidence of the Effects of Air Pollution on Crime, with Salvador Lurbé and Prasiddha Shakya.
\item The Effect of Leaded Gasoline on Infant Health: Evidence from NASCAR Fuel Transition, with Yuulin An and Sammy Zahran.
\item Maternal Lead Exposure and Birth Outcomes: Evidence from Natural Experiments in the Phase-out of Leaded Gasoline, with Sammy Zahran, Christopher Keyes, and Yuulin An.
\end{enumerate}

\textbf{Work in Progress}
\begin{enumerate}[leftmargin=*, label={[\arabic*]}]
    \item Lead Exposure and Heart-Disease Mortality in the United
States, with Christopher Keyes, Bruce Lanphear, and Sammy Zahran.
    \item Tip Credit Effects on Employment, Earnings, and Establishments, with Vinicius Curti Cícero and Sammy Zahran.
    \item The Morning Advantage: Differential Returns to Sunlight Exposure on Well-being, with Sammy Zahran and Ray Miller.
    \item Excess Emissions and Infant Health: Evidence from Texas, with Susan Averett.
    \item Urban Heat Island and Birth Complications, with Yuulin An and Tim Komarek.
    \item Bringing Introductory Economics to Life: A Scaffolded
Research Paper as Authentic Assessment in
Introductory Economics, with Teresa Perry, Fatih K\i r\c{s}anl\i, and Kenese Io.
\end{enumerate}

\section{Teaching Experience}

\textbf{Lafayette College}\\
ECON 215: Health Economics \hfill{FA 2025}\\
ECON 346: Economic Development \hfill{FA 2024, SP 2025, FA 2025, SP 2026}\\
ECON 251: Intermediate Microeconomics \hfill{FA 2023, SP 2024, FA 2024, SP 2025, SP 2026}

\vspace{0.18cm}

\textbf{Colorado State University}\\
ECON 202: Principles of Microeconomics \hfill{FA 2017, FA 2019, SM 2020, FA 2021}\\
\strut\hfill\hfill{SP 2022, FA 2022, SP 2023}\\
ECON 204: Principles of Macroeconomics \hfill{SP 2018, FA 2018, SP 2019}\\
\strut\hfill\hfill{SP 2020, FA 2020}\\
ECON 306: Intermediate Microeconomics \hfill{FA 2021, SP 2022}\\
ECON 304: Intermediate Macroeconomics \hfill{SP 2021}\\
ECON 335: Introduction to Econometrics \hfill{SM 2019}\\
ECON 460: Economic Development \hfill{FA 2021}

\section{Research Advising}

\textbf{Honors Thesis Advising}\\
Daniel Colden ('26) - Economics and History (Primary Advisor)\\
Benjamin Risley ('26) - Government and Law, Economics (Second Reader)

\vspace{0.18cm}

\textbf{Independent Study}\\
Isabel Berkeley ('25) \hfill{Spring 2025}\\
Xinyuan Liang ('27) \hfill{Spring 2025}\\
Yi Luo ('26) \hfill{Spring 2025}\\
Justin Fretz ('25) \hfill{Spring 2025}

\vspace{0.18cm}

\textbf{EXCEL Scholars/Bergh Fellows/Research Assistants}\\
Fiorella Garcia Sanchez ('27) \hfill{Summer 2026}\\
Yi Luo ('26) \hfill{Fall 2025}\\
Ava Sydell ('27) \hfill{Summer 2025}\\
Daniel Colden ('26) \hfill{Winter 2025}\\
Naya Kurdy ('25) \hfill{Fall 2024, Spring 2025}\\
Vanika Sok ('26) \hfill{Summer 2024, Fall 2024}


\section{College Service}
Artificial Intelligence Club Advisor \hfill{Summer 2025 -- Present}\\
International Faculty \& Staff Community of Practice Board Member
\hfill{Spring 2025 -- Present}

\section{Department Service}
Scholarship Revision Working Group \hfill{Fall 2025 -- Present}\\
Co-organizer Department Honors Program \hfill{Fall 2024 -- Present}

\section{Honors and Awards}

Student Government Superior Teaching Awards Nominee, Lafayette College \hfill{2024}\\
Graduate Research Assistantship, Colorado State University \hfill{2022}\\
Competition Committee Member, AFIT-AFEE 16th Annual Student Scholars Award \hfill{2022}\\
Best Paper Award, AFIT-AFEE 16th Annual Student Scholars Award \hfill{2021}\\
Graduate Teaching Assistantship, Colorado State University \hfill{2017 -- 2023}\\
Colorado College Financial Aid Award \hfill{2013 -- 2017}\\
Davis United World College Scholars Scholarship Award \hfill{2013 -- 2017}\\
United World College of Southeast Asia Scholarship Award \hfill{2008 -- 2013}

\section{Conferences}
Eastern Economic Association, La Romana, Dominican Republic \hfill{2026}\\
Association for Public Policy Analysis and Management, Seattle, WA \hfill{2025}\\
Southern Economic Association 95th Annual Meeting, Tampa, FL \hfill{2025}\\
14th Annual Conference on Teaching and Research in Economic Education, Denver \hfill{2025}\\
Southern Economic Association 94th Annual Meeting, Washington, D.C. \hfill{2024}\\
70th NARSC Meetings, San Diego, CA \hfill{2023}\\
The 3rd Annual Conference of the Western Social Science Association 2021 (virtual) \hfill{2021}

\section{Other Conference Activities}
Eastern Economic Association, La Romana, Dominican Republic, \textit{Discussant} \hfill{2026}\\
ASSA Annual Meeting, Philadelphia, PA, \textit{Session Chair: Artificial Intelligence} \hfill{2026}\\
Southern Economic Association 94th Annual Meeting, Washington, D.C., \textit{Discussant} \hfill{2024}\\
70th NARSC Meetings, San Diego, CA, \textit{Discussant} \hfill{2023}

\section{Workshops}
7th Annual Southeastern Micro Labor Workshop, FRB Atlanta, Orlando \hfill{2025}\\
6th Annual Southeastern Micro Labor Workshop, FRB Atlanta, Clemson \hfill{2024}

\clearpage

\section{Media Mentions}
Huss, Phoebe. \href{https://calmatters.org/education/2026/03/feel-free-kratom-california-university-public-health-ban/}{``Once given out at USC, this banned, opioid-like product is still cropping up in California.''} \textit{CalMatters}, March 17, 2026.

\vspace{0.18cm}

Reddy, Sumathi. \href{https://www.wsj.com/health/wellness/kratom-supplement-safety-b63d0573?gaa_at=eafs&gaa_n=ASWzDAhrqqlrzhaJxFkqqPddp5QD6nUXkxFc3JjdBDQpvomtV5qNlhN3v1kV0kvbJP8%3D&gaa_ts=68a0f048&gaa_sig=_AhqwvecENFGUuDLMS-1FNxAXY9ZoNKEGgc5P7qmZeDH4grCczT-wpgmwMGEAzP40eQJJf22qVj-6zBg08jp7g%3D%3D}{``What You Need to Know About Kratom.''} \textit{Wall Street Journal}, August 16, 2025.

\vspace{0.18cm}

\href{https://kratomsobriety.podbean.com/e/e46-teresa-perry-phd-academic-paper-on-rise-of-kratom-tonic-products/}{``Teresa Perry, PhD: Academic Paper on the Rise of Kratom Tonic Products.''} \textit{Kratom Sobriety Podcast}, episode 46.

\section{Invited Talks}
Colorado College Economic Department Seminar Series \hfill{2026}\\
Dickinson College Economic Department Seminar Series \hfill{2025}\\
AI in Economics Seminar Series at Royal Holloway, University of London (virtual) \hfill{2025}\\
Keynote Speaker, APIME Graduation Celebration at Lafayette College \hfill{2025}\\
Faculty Features: A Roundtable Celebrating Lafayette Faculty Scholarship and
Creativity \hfill{2025}\\
Asian Cultural Association at Lafayette College \hfill{2024, 2025}\\
The Hanson Center for Inclusive STEM Education at Lafayette College \hfill{2024}\\
University of Wyoming, Knox College, University of New Hampshire \hfill{2023}

\section{Skills and Credentials}
\textbf{Programming/Software}\\
Proficient in: Python, R, Stata, MySQL, Git/GitHub

\vspace{0.18cm}

\textbf{Certifications}\\
Good Clinical Practice Training for Social and Behavioral Research, Tools for Data Science, Python for Data Science, Python for Data Science \& AI,
Data Science Methodology, Database \& SQL for Data Science, Data Analysis with
Python, Machine Learning with Python, Data Visualization with Python, Python
Project for Data Science

\section{Professional Affiliations}

American Economic Association, American Society of Health Economists

\section{Professional Service}
%Co-facilitator in the teaching workshop about AI at the ASSA  \hfill{Jan. 3-5, 2026}\\
Referee for: \emph{International Journal of Mental Health and Addiction} (2), \emph{Regulation \& Governance} (2), \emph{Eastern Economic Journal}, \emph{Journal of Family and Economic Issues}, \emph{Economics and Human Biology} (3), \emph{Energy Economics} (4), \emph{World Development}

\vspace{0.18cm}

External reviewer: Ph.D. Dissertation at Indian Institute of Technology (IIT) Kanpur

%\section{References}

%Available upon request

\end{document}
